---
title: "Untitled"
author: "Aydan Askarova"
date: "28/06/2023"
output: html_document
---

title: "pheatmap_cell_specific"
author: "Aydan Askarova"
date: "27/06/2023"
output: html_document
---
```{r packaged}

library(pheatmap)
library(RColorBrewer)
library(data.table)
library(plyr)
library(dplyr)
library(UpSetR)
library(purrr)
library(ComplexHeatmap)
library(ggplot2)

```
#Cell names and disease names 
```{r}
#Cell names and disease names 
#type<-c("AD", "MS", "ALS", "PD", "SCZ")
cell<- c("Microglia_interactome", "Neuronal_interactome", "Oligo_interactome")
type<-c("AD_Jansen2019", "AD_Kunkle2019", "PD_Nalls2019proxy", "MS_Andlauer2016", "ALS_Rheenen2021", "SCZ_Trubetskoy2022", "Longevity_Deelan201990th")
#Directories to save the files 
dir<-"~/HMAGMA_Protocol/HMAGMA_output_v3/original/"
outdir<-"~/HMAGMA_Protocol/output_annotation_v4/"

for(c in 1:length(cell)){
  for(t in 1:length(type)){
    
    load(file= paste0(outdir, cell[c], "_",  type[t], "_fdr005_output_genes_v4.rda")) #diseasemat_names
    diseasemat_names<-diseasemat_names[,c("gene_name", "gene_fdr")]
    #diseasemat_names<- diseasemat_names %>% filter(diseasemat_names$gene_fdr<5e-8)
    #diseasemat_names<-diseasemat_names[1:50,] #per disease heatmap
    colnames(diseasemat_names)[2]<-paste0(cell[c], "_", type[t])
    assign(paste0(type[t], "_", cell[c]), diseasemat_names)
  }
}

for(c in 1:length(cell)){
  for(t in 1:length(type)){
    
    load(file= paste0(outdir, cell[c], "_",  type[t], "_fdr005_output_genes_v4.rda")) #diseasemat_names
    diseasemat_names<-diseasemat_names[,c("gene_name", "gene_fdr")]
    diseasemat_names<- diseasemat_names %>% filter(diseasemat_names$gene_fdr<5e-8)
    #diseasemat_names<-diseasemat_names[1:50,] #per disease heatmap
    colnames(diseasemat_names)[2]<-paste0(cell[c], "_", type[t])
    assign(paste0(type[t], "_5e8", cell[c]), diseasemat_names)
  }
}

type<-c("SCZ_Trubetskoy2022") #.v2 

for(c in 1:length(cell)){
  for(t in 1:length(type)){
    
    load(file= paste0(outdir, cell[c], "_",  type[t], "_fdr005_output_genes_v4.rda")) #diseasemat_names
    diseasemat_names<-diseasemat_names[,c("gene_name", "gene_fdr")]
    diseasemat_names<- diseasemat_names %>% filter(diseasemat_names$gene_fdr<5e-12)
    #diseasemat_names<-diseasemat_names[1:50,]  #per disease heatmap
    colnames(diseasemat_names)[2]<-paste0(cell[c], "_", type[t])
    assign(paste0(type[t], "_5e12", cell[c]), diseasemat_names)
  }
}
```


#UPSET PLOT -INTERSECTION OF ALL GENES in NUMBERS
```{r}
lt = list(AD_Jansen = AD_Jansen2019_Microglia_interactome$gene_name, PD=PD_Nalls2019proxy_Microglia_interactome$gene_name, MS = MS_Andlauer2016_Microglia_interactome$gene_name, ALS = ALS_Rheenen2021_Microglia_interactome$gene_name, SCZ = SCZ_Trubetskoy2022_5e8Microglia_interactome$gene_name)

lt_oligo = list(AD_Jasen = AD_Jansen2019_Oligo_interactome$gene_name, PD=PD_Nalls2019proxy_Oligo_interactome$gene_name, MS = MS_Andlauer2016_Oligo_interactome$gene_name, ALS = ALS_Rheenen2021_Oligo_interactome$gene_name, SCZ = SCZ_Trubetskoy2022_5e8Oligo_interactome$gene_name)

lt_neun = list(AD_Jansen = AD_Jansen2019_Neuronal_interactome$gene_name, PD=PD_Nalls2019proxy_Neuronal_interactome$gene_name, MS = MS_Andlauer2016_Neuronal_interactome$gene_name, ALS = ALS_Rheenen2021_Neuronal_interactome$gene_name, SCZ = SCZ_Trubetskoy2022_5e8Neuronal_interactome$gene_name)

pu1 <- upset(fromList(lt), order.by = "freq", sets.bar.color = c("midnightblue","olivedrab3", "orangered4", "darkorange2", "slateblue3"), mainbar.y.label = "Gene Count", sets.x.label = "Gene Count per Disease")

oligo <- upset(fromList(lt_oligo), order.by = "freq", sets.bar.color = c("olivedrab3", "orangered4", "darkorange2",  "midnightblue",  "slateblue3"), mainbar.y.label = "Gene Count", sets.x.label = "Gene Count per Disease")

neun <- upset(fromList(lt_neun), order.by = "freq", sets.bar.color = c("olivedrab3", "darkorange2",  "slateblue3", "midnightblue", "orangered4"), mainbar.y.label = "Gene Count", sets.x.label = "Gene Count per Disease")

```

#AD - Looking for overlaps of genes between diseases and <5e-8
```{r}

join1<-join(x = AD_Jansen2019_5e8Microglia_interactome, y = AD_Kunkle2019_Microglia_interactome, "gene_name", type="left")
join2<-join(x = join1, y = PD_Nalls2019proxy_Microglia_interactome, "gene_name", type="left")
#join3<-join(x = join2, y = LBD_chia2021_Microglia_interactome, "gene_name", type="left")
join4<-join(x = join2, y = MS_Andlauer2016_Microglia_interactome, "gene_name", type="left")
join5<-join(x = join4, y = ALS_Rheenen2021_Microglia_interactome, "gene_name", type="left")
join6<-join(x = join5, y = SCZ_Trubetskoy2022_Microglia_interactome, "gene_name", type="left")

AD_Jansen2019_5e8Microglia_interactome_overlap<-join6


join1<-join(x = AD_Jansen2019_5e8Neuronal_interactome, y = AD_Kunkle2019_Neuronal_interactome, "gene_name", type="left")
join2<-join(x = join1, y = PD_Nalls2019proxy_Neuronal_interactome, "gene_name", type="left")
#join3<-join(x = join2, y = LBD_chia2021_Neuronal_interactome, "gene_name", type="left")
join4<-join(x = join2, y = MS_Andlauer2016_Neuronal_interactome, "gene_name", type="left")
join5<-join(x = join4, y = ALS_Rheenen2021_Neuronal_interactome, "gene_name", type="left")
join6<-join(x = join5, y = SCZ_Trubetskoy2022_Neuronal_interactome, "gene_name", type="left")

AD_Jansen2019_5e8Neuronal_interactome_overlap<-join6

join1<-join(x = AD_Jansen2019_5e8Oligo_interactome, y = AD_Kunkle2019_Oligo_interactome, "gene_name", type="left")
join2<-join(x = join1, y = PD_Nalls2019proxy_Oligo_interactome, "gene_name", type="left")
#join3<-join(x = join2, y = LBD_chia2021_Oligo_interactome, "gene_name", type="left")
join4<-join(x = join2, y = MS_Andlauer2016_Oligo_interactome, "gene_name", type="left")
join5<-join(x = join4, y = ALS_Rheenen2021_Oligo_interactome, "gene_name", type="left")
join6<-join(x = join5, y = SCZ_Trubetskoy2022_Oligo_interactome, "gene_name", type="left")

AD_Jansen2019_5e8Oligo_interactome_overlap<-join6



```

#AD_Kunkle- Looking for overlaps of genes between diseases and <5e-8
```{r}
join1<-join(x = AD_Kunkle2019_5e8Microglia_interactome, y = AD_Jansen2019_Microglia_interactome, "gene_name", type="left")
join2<-join(x = join1, y = PD_Nalls2019proxy_Microglia_interactome, "gene_name", type="left")
#join3<-join(x = join2, y = LBD_chia2021_Microglia_interactome, "gene_name", type="left")
join4<-join(x = join2, y = MS_Andlauer2016_Microglia_interactome, "gene_name", type="left")
join5<-join(x = join4, y = ALS_Rheenen2021_Microglia_interactome, "gene_name", type="left")
join6<-join(x = join5, y = SCZ_Trubetskoy2022_Microglia_interactome, "gene_name", type="left")

AD_Kunkle2019_5e8Microglia_interactome_overlap<-join6

join1<-join(x = AD_Kunkle2019_5e8Neuronal_interactome, y = AD_Jansen2019_Neuronal_interactome, "gene_name", type="left")
join2<-join(x = join1, y = PD_Nalls2019proxy_Neuronal_interactome, "gene_name", type="left")
#join3<-join(x = join2, y = LBD_chia2021_Neuronal_interactome, "gene_name", type="left")
join4<-join(x = join2, y = MS_Andlauer2016_Neuronal_interactome, "gene_name", type="left")
join5<-join(x = join4, y = ALS_Rheenen2021_Neuronal_interactome, "gene_name", type="left")
join6<-join(x = join5, y = SCZ_Trubetskoy2022_Neuronal_interactome, "gene_name", type="left")

AD_Kunkle2019_5e8Neuronal_interactome_overlap<-join6

join1<-join(x = AD_Kunkle2019_5e8Oligo_interactome, y = AD_Jansen2019_Oligo_interactome, "gene_name", type="left")
join2<-join(x = join1, y = PD_Nalls2019proxy_Oligo_interactome, "gene_name", type="left")
#join3<-join(x = join2, y = LBD_chia2021_Oligo_interactome, "gene_name", type="left")
join4<-join(x = join2, y = MS_Andlauer2016_Oligo_interactome, "gene_name", type="left")
join5<-join(x = join4, y = ALS_Rheenen2021_Oligo_interactome, "gene_name", type="left")
join6<-join(x = join5, y = SCZ_Trubetskoy2022_Oligo_interactome, "gene_name", type="left")

AD_Kunkle2019_5e8Oligo_interactome_overlap<-join6

```

#PD_Nalls2019proxy- Looking for overlaps of genes between diseases and <5e-8
```{r}
join1<-join(x = PD_Nalls2019proxy_5e8Microglia_interactome, y = AD_Jansen2019_Microglia_interactome, "gene_name", type="left")
join2<-join(x = join1, y = AD_Kunkle2019_Microglia_interactome, "gene_name", type="left")
#join3<-join(x = join2, y = LBD_chia2021_Microglia_interactome, "gene_name", type="left")
join4<-join(x = join2, y = MS_Andlauer2016_Microglia_interactome, "gene_name", type="left")
join5<-join(x = join4, y = ALS_Rheenen2021_Microglia_interactome, "gene_name", type="left")
join6<-join(x = join5, y = SCZ_Trubetskoy2022_Microglia_interactome, "gene_name", type="left")

PD_Nalls2019proxy_5e8Microglia_interactome_overlap<-join6

join1<-join(x = PD_Nalls2019proxy_5e8Neuronal_interactome, y = AD_Jansen2019_Neuronal_interactome, "gene_name", type="left")
join2<-join(x = join1, y = AD_Kunkle2019_Neuronal_interactome, "gene_name", type="left")
#join3<-join(x = join2, y = LBD_chia2021_Neuronal_interactome, "gene_name", type="left")
join4<-join(x = join2, y = MS_Andlauer2016_Neuronal_interactome, "gene_name", type="left")
join5<-join(x = join4, y = ALS_Rheenen2021_Neuronal_interactome, "gene_name", type="left")
join6<-join(x = join5, y = SCZ_Trubetskoy2022_Neuronal_interactome, "gene_name", type="left")

PD_Nalls2019proxy_5e8Neuronal_interactome_overlap<-join6

join1<-join(x = PD_Nalls2019proxy_5e8Oligo_interactome, y = AD_Jansen2019_Oligo_interactome, "gene_name", type="left")
join2<-join(x = join1, y = AD_Kunkle2019_Oligo_interactome, "gene_name", type="left")
#join3<-join(x = join2, y = LBD_chia2021_Oligo_interactome, "gene_name", type="left")
join4<-join(x = join2, y = MS_Andlauer2016_Oligo_interactome, "gene_name", type="left")
join5<-join(x = join4, y = ALS_Rheenen2021_Oligo_interactome, "gene_name", type="left")
join6<-join(x = join5, y = SCZ_Trubetskoy2022_Oligo_interactome, "gene_name", type="left")

PD_Nalls2019proxy_5e8Oligo_interactome_overlap<-join6
```

#LBD_chia2021- Looking for overlaps of genes between diseases and <5e-8
```{r}
join1<-join(x = LBD_chia2021_5e8Microglia_interactome, y = AD_Jansen2019_Microglia_interactome, "gene_name", type="left")
join2<-join(x = join1, y = AD_Kunkle2019_Microglia_interactome, "gene_name", type="left")
join3<-join(x = join2, y = PD_Nalls2019proxy_Microglia_interactome, "gene_name", type="left")
join4<-join(x = join3, y = MS_Andlauer2016_Microglia_interactome, "gene_name", type="left")
join5<-join(x = join4, y = ALS_Rheenen2021_Microglia_interactome, "gene_name", type="left")
join6<-join(x = join5, y = SCZ_Trubetskoy2022_Microglia_interactome, "gene_name", type="left")

LBD_chia2021_5e8Microglia_interactome_overlap<-join6

join1<-join(x = LBD_chia2021_5e8Neuronal_interactome, y = AD_Jansen2019_Neuronal_interactome, "gene_name", type="left")
join2<-join(x = join1, y = AD_Kunkle2019_Neuronal_interactome, "gene_name", type="left")
join3<-join(x = join2, y = PD_Nalls2019proxy_Neuronal_interactome, "gene_name", type="left")
join4<-join(x = join3, y = MS_Andlauer2016_Neuronal_interactome, "gene_name", type="left")
join5<-join(x = join4, y = ALS_Rheenen2021_Neuronal_interactome, "gene_name", type="left")
join6<-join(x = join5, y = SCZ_Trubetskoy2022_Neuronal_interactome, "gene_name", type="left")

LBD_chia2021_5e8Neuronal_interactome_overlap<-join6

join1<-join(x = LBD_chia2021_5e8Oligo_interactome, y = AD_Jansen2019_Oligo_interactome, "gene_name", type="left")
join2<-join(x = join1, y = AD_Kunkle2019_Oligo_interactome, "gene_name", type="left")
join3<-join(x = join2, y = PD_Nalls2019proxy_Oligo_interactome, "gene_name", type="left")
join4<-join(x = join3, y = MS_Andlauer2016_Oligo_interactome, "gene_name", type="left")
join5<-join(x = join4, y = ALS_Rheenen2021_Oligo_interactome, "gene_name", type="left")
join6<-join(x = join5, y = SCZ_Trubetskoy2022_Oligo_interactome, "gene_name", type="left")

LBD_chia2021_5e8Oligo_interactome_overlap<-join6
```

#MS_Andlauer2016- Looking for overlaps of genes between diseases and <5e-8

```{r}
join1<-join(x = MS_Andlauer2016_5e8Microglia_interactome, y = AD_Jansen2019_Microglia_interactome, "gene_name", type="left")
join2<-join(x = join1, y = AD_Kunkle2019_Microglia_interactome, "gene_name", type="left")
join3<-join(x = join2, y = PD_Nalls2019proxy_Microglia_interactome, "gene_name", type="left")
#join4<-join(x = join3, y = LBD_chia2021_Microglia_interactome, "gene_name", type="left")
join5<-join(x = join3, y = ALS_Rheenen2021_Microglia_interactome, "gene_name", type="left")
join6<-join(x = join5, y = SCZ_Trubetskoy2022_Microglia_interactome, "gene_name", type="left")

MS_Andlauer2016_5e8Microglia_interactome_overlap<-join6

join1<-join(x = MS_Andlauer2016_5e8Neuronal_interactome, y = AD_Jansen2019_Neuronal_interactome, "gene_name", type="left")
join2<-join(x = join1, y = AD_Kunkle2019_Neuronal_interactome, "gene_name", type="left")
join3<-join(x = join2, y = PD_Nalls2019proxy_Neuronal_interactome, "gene_name", type="left")
#join4<-join(x = join3, y = LBD_chia2021_Neuronal_interactome, "gene_name", type="left")
join5<-join(x = join3, y = ALS_Rheenen2021_Neuronal_interactome, "gene_name", type="left")
join6<-join(x = join5, y = SCZ_Trubetskoy2022_Neuronal_interactome, "gene_name", type="left")

MS_Andlauer2016_5e8Neuronal_interactome_overlap<-join6

join1<-join(x = MS_Andlauer2016_5e8Oligo_interactome, y = AD_Jansen2019_Oligo_interactome, "gene_name", type="left")
join2<-join(x = join1, y = AD_Kunkle2019_Oligo_interactome, "gene_name", type="left")
join3<-join(x = join2, y = PD_Nalls2019proxy_Oligo_interactome, "gene_name", type="left")
#join4<-join(x = join3, y = LBD_chia2021_Oligo_interactome, "gene_name", type="left")
join5<-join(x = join3, y = ALS_Rheenen2021_Oligo_interactome, "gene_name", type="left")
join6<-join(x = join5, y = SCZ_Trubetskoy2022_Oligo_interactome, "gene_name", type="left")

MS_Andlauer2016_5e8Oligo_interactome_overlap<-join6
```

#ALS_Rheenen2021- Looking for overlaps of genes between diseases and <5e-8

```{r}
join1<-join(x = ALS_Rheenen2021_5e8Microglia_interactome, y = AD_Jansen2019_Microglia_interactome, "gene_name", type="left")
join2<-join(x = join1, y = AD_Kunkle2019_Microglia_interactome, "gene_name", type="left")
join3<-join(x = join2, y = PD_Nalls2019proxy_Microglia_interactome, "gene_name", type="left")
#join4<-join(x = join3, y = LBD_chia2021_Microglia_interactome, "gene_name", type="left")
join5<-join(x = join3, y = MS_Andlauer2016_Microglia_interactome, "gene_name", type="left")
join6<-join(x = join5, y = SCZ_Trubetskoy2022_Microglia_interactome, "gene_name", type="left")

ALS_Rheenen2021_5e8Microglia_interactome_overlap<-join6

join1<-join(x = ALS_Rheenen2021_5e8Neuronal_interactome, y = AD_Jansen2019_Neuronal_interactome, "gene_name", type="left")
join2<-join(x = join1, y = AD_Kunkle2019_Neuronal_interactome, "gene_name", type="left")
join3<-join(x = join2, y = PD_Nalls2019proxy_Neuronal_interactome, "gene_name", type="left")
#join4<-join(x = join3, y = LBD_chia2021_Neuronal_interactome, "gene_name", type="left")
join5<-join(x = join3, y = MS_Andlauer2016_Neuronal_interactome, "gene_name", type="left")
join6<-join(x = join5, y = SCZ_Trubetskoy2022_Neuronal_interactome, "gene_name", type="left")

ALS_Rheenen2021_5e8Neuronal_interactome_overlap<-join6

join1<-join(x = ALS_Rheenen2021_5e8Oligo_interactome, y = AD_Jansen2019_Oligo_interactome, "gene_name", type="left")
join2<-join(x = join1, y = AD_Kunkle2019_Oligo_interactome, "gene_name", type="left")
join3<-join(x = join2, y = PD_Nalls2019proxy_Oligo_interactome, "gene_name", type="left")
#join4<-join(x = join3, y = LBD_chia2021_Oligo_interactome, "gene_name", type="left")
join5<-join(x = join3, y = MS_Andlauer2016_Oligo_interactome, "gene_name", type="left")
join6<-join(x = join5, y = SCZ_Trubetskoy2022_Oligo_interactome, "gene_name", type="left")

ALS_Rheenen2021_5e8Oligo_interactome_overlap<-join6

```

#SCZ_Trubetskoy2022- Looking for overlaps of genes between diseases and <5e-8

```{r}
join1<-join(x = SCZ_Trubetskoy2022_5e12Microglia_interactome, y = AD_Jansen2019_Microglia_interactome, "gene_name", type="left")
join2<-join(x = join1, y = AD_Kunkle2019_Microglia_interactome, "gene_name", type="left")
join3<-join(x = join2, y = PD_Nalls2019proxy_Microglia_interactome, "gene_name", type="left")
#join4<-join(x = join3, y = LBD_chia2021_Microglia_interactome, "gene_name", type="left")
join5<-join(x = join3, y = MS_Andlauer2016_Microglia_interactome, "gene_name", type="left")
join6<-join(x = join5, y = ALS_Rheenen2021_Microglia_interactome, "gene_name", type="left")

SCZ_Trubetskoy2022_5e12Microglia_interactome_overlap<-join6

join1<-join(x = SCZ_Trubetskoy2022_5e12Neuronal_interactome, y = AD_Jansen2019_Neuronal_interactome, "gene_name", type="left")
join2<-join(x = join1, y = AD_Kunkle2019_Neuronal_interactome, "gene_name", type="left")
join3<-join(x = join2, y = PD_Nalls2019proxy_Neuronal_interactome, "gene_name", type="left")
#join4<-join(x = join3, y = LBD_chia2021_Neuronal_interactome, "gene_name", type="left")
join5<-join(x = join3, y = MS_Andlauer2016_Neuronal_interactome, "gene_name", type="left")
join6<-join(x = join5, y = ALS_Rheenen2021_Neuronal_interactome, "gene_name", type="left")

SCZ_Trubetskoy2022_5e12Neuronal_interactome_overlap<-join6

join1<-join(x = SCZ_Trubetskoy2022_5e12Oligo_interactome, y = AD_Jansen2019_Oligo_interactome, "gene_name", type="left")
join2<-join(x = join1, y = AD_Kunkle2019_Oligo_interactome, "gene_name", type="left")
join3<-join(x = join2, y = PD_Nalls2019proxy_Oligo_interactome, "gene_name", type="left")
#join4<-join(x = join3, y = LBD_chia2021_Oligo_interactome, "gene_name", type="left")
join5<-join(x = join3, y = MS_Andlauer2016_Oligo_interactome, "gene_name", type="left")
join6<-join(x = join5, y = ALS_Rheenen2021_Oligo_interactome, "gene_name", type="left")

SCZ_Trubetskoy2022_5e12Oligo_interactome_overlap<-join6
```


#AD_Jansen - combining all genes per disease together - the ones that overap with other diseases and 5e-8
```{r}
#micrglia
AD_AD<-data.frame(gene_name=AD_Jansen2019_5e8Microglia_interactome_overlap$gene_name, Microglia_interactome_AD_Jansen2019 = AD_Jansen2019_5e8Microglia_interactome_overlap$Microglia_interactome_AD_Jansen2019)

AD_AD_k<-data.frame(gene_name=AD_Kunkle2019_5e8Microglia_interactome_overlap$gene_name, Microglia_interactome_AD_Jansen2019 = AD_Kunkle2019_5e8Microglia_interactome_overlap$Microglia_interactome_AD_Jansen2019)

AD_PD<-data.frame(gene_name=PD_Nalls2019proxy_5e8Microglia_interactome_overlap$gene_name, Microglia_interactome_AD_Jansen2019 = PD_Nalls2019proxy_5e8Microglia_interactome_overlap$Microglia_interactome_AD_Jansen2019)

#AD_LBD<-data.frame(gene_name=LBD_chia2021_5e8Microglia_interactome_overlap$gene_name, Microglia_interactome_AD_Jansen2019 = LBD_chia2021_5e8Microglia_interactome_overlap$Microglia_interactome_AD_Jansen2019)

AD_MS<-data.frame(gene_name=MS_Andlauer2016_5e8Microglia_interactome_overlap$gene_name, Microglia_interactome_AD_Jansen2019 = MS_Andlauer2016_5e8Microglia_interactome_overlap$Microglia_interactome_AD_Jansen2019)

AD_ALS<-data.frame(gene_name=ALS_Rheenen2021_5e8Microglia_interactome_overlap$gene_name, Microglia_interactome_AD_Jansen2019 = ALS_Rheenen2021_5e8Microglia_interactome_overlap$Microglia_interactome_AD_Jansen2019)

AD_SCZ<-data.frame(gene_name=SCZ_Trubetskoy2022_5e12Microglia_interactome_overlap$gene_name, Microglia_interactome_AD_Jansen2019 = SCZ_Trubetskoy2022_5e12Microglia_interactome_overlap$Microglia_interactome_AD_Jansen2019)


AD_pu1<-rbind(AD_AD, AD_AD_k, AD_PD, AD_MS, AD_ALS, AD_SCZ)

#neurons 

AD_AD<-data.frame(gene_name=AD_Jansen2019_5e8Neuronal_interactome_overlap$gene_name, Neuronal_interactome_AD_Jansen2019 = AD_Jansen2019_5e8Neuronal_interactome_overlap$Neuronal_interactome_AD_Jansen2019)

AD_AD_k<-data.frame(gene_name=AD_Kunkle2019_5e8Neuronal_interactome_overlap$gene_name, Neuronal_interactome_AD_Jansen2019 = AD_Kunkle2019_5e8Neuronal_interactome_overlap$Neuronal_interactome_AD_Jansen2019)

AD_PD<-data.frame(gene_name=PD_Nalls2019proxy_5e8Neuronal_interactome_overlap$gene_name, Neuronal_interactome_AD_Jansen2019 = PD_Nalls2019proxy_5e8Neuronal_interactome_overlap$Neuronal_interactome_AD_Jansen2019)

#AD_LBD<-data.frame(gene_name=LBD_chia2021_5e8Neuronal_interactome_overlap$gene_name, Neuronal_interactome_AD_Jansen2019 = LBD_chia2021_5e8Neuronal_interactome_overlap$Neuronal_interactome_AD_Jansen2019)

AD_MS<-data.frame(gene_name=MS_Andlauer2016_5e8Neuronal_interactome_overlap$gene_name, Neuronal_interactome_AD_Jansen2019 = MS_Andlauer2016_5e8Neuronal_interactome_overlap$Neuronal_interactome_AD_Jansen2019)

AD_ALS<-data.frame(gene_name=ALS_Rheenen2021_5e8Neuronal_interactome_overlap$gene_name, Neuronal_interactome_AD_Jansen2019 = ALS_Rheenen2021_5e8Neuronal_interactome_overlap$Neuronal_interactome_AD_Jansen2019)

AD_SCZ<-data.frame(gene_name=SCZ_Trubetskoy2022_5e12Neuronal_interactome_overlap$gene_name, Neuronal_interactome_AD_Jansen2019 = SCZ_Trubetskoy2022_5e12Neuronal_interactome_overlap$Neuronal_interactome_AD_Jansen2019)


AD_neun<-rbind(AD_AD, AD_AD_k, AD_PD, AD_MS, AD_ALS, AD_SCZ)

#olig

AD_AD<-data.frame(gene_name=AD_Jansen2019_5e8Oligo_interactome_overlap$gene_name, Oligo_interactome_AD_Jansen2019 = AD_Jansen2019_5e8Oligo_interactome_overlap$Oligo_interactome_AD_Jansen2019)

AD_AD_k<-data.frame(gene_name=AD_Kunkle2019_5e8Oligo_interactome_overlap$gene_name, Oligo_interactome_AD_Jansen2019 = AD_Kunkle2019_5e8Oligo_interactome_overlap$Oligo_interactome_AD_Jansen2019)

AD_PD<-data.frame(gene_name=PD_Nalls2019proxy_5e8Oligo_interactome_overlap$gene_name, Oligo_interactome_AD_Jansen2019 = PD_Nalls2019proxy_5e8Oligo_interactome_overlap$Oligo_interactome_AD_Jansen2019)

#AD_LBD<-data.frame(gene_name=LBD_chia2021_5e8Oligo_interactome_overlap$gene_name, Oligo_interactome_AD_Jansen2019 = LBD_chia2021_5e8Oligo_interactome_overlap$Oligo_interactome_AD_Jansen2019)

AD_MS<-data.frame(gene_name=MS_Andlauer2016_5e8Oligo_interactome_overlap$gene_name, Oligo_interactome_AD_Jansen2019 = MS_Andlauer2016_5e8Oligo_interactome_overlap$Oligo_interactome_AD_Jansen2019)

AD_ALS<-data.frame(gene_name=ALS_Rheenen2021_5e8Oligo_interactome_overlap$gene_name, Oligo_interactome_AD_Jansen2019 = ALS_Rheenen2021_5e8Oligo_interactome_overlap$Oligo_interactome_AD_Jansen2019)

AD_SCZ<-data.frame(gene_name=SCZ_Trubetskoy2022_5e12Oligo_interactome_overlap$gene_name, Oligo_interactome_AD_Jansen2019 = SCZ_Trubetskoy2022_5e12Oligo_interactome_overlap$Oligo_interactome_AD_Jansen2019)


AD_olig<-rbind(AD_AD, AD_AD_k, AD_PD, AD_MS, AD_ALS, AD_SCZ)
```

#AD_Kunkle - combining all genes per disease together - the ones that overap with other diseases and 5e-8
```{r}
#micrglia
ADk_ADk<-data.frame(gene_name=AD_Kunkle2019_5e8Microglia_interactome_overlap$gene_name, Microglia_interactome_AD_Kunkle2019 = AD_Kunkle2019_5e8Microglia_interactome_overlap$Microglia_interactome_AD_Kunkle2019)

ADk_AD<-data.frame(gene_name=AD_Jansen2019_5e8Microglia_interactome_overlap$gene_name, Microglia_interactome_AD_Kunkle2019 = AD_Jansen2019_5e8Microglia_interactome_overlap$Microglia_interactome_AD_Kunkle2019)

ADk_PD<-data.frame(gene_name=PD_Nalls2019proxy_5e8Microglia_interactome_overlap$gene_name, Microglia_interactome_AD_Kunkle2019 = PD_Nalls2019proxy_5e8Microglia_interactome_overlap$Microglia_interactome_AD_Kunkle2019)

#ADk_LBD<-data.frame(gene_name=LBD_chia2021_5e8Microglia_interactome_overlap$gene_name, Microglia_interactome_AD_Kunkle2019 = LBD_chia2021_5e8Microglia_interactome_overlap$Microglia_interactome_AD_Kunkle2019)

ADk_MS<-data.frame(gene_name=MS_Andlauer2016_5e8Microglia_interactome_overlap$gene_name, Microglia_interactome_AD_Kunkle2019 = MS_Andlauer2016_5e8Microglia_interactome_overlap$Microglia_interactome_AD_Kunkle2019)

ADk_ALS<-data.frame(gene_name=ALS_Rheenen2021_5e8Microglia_interactome_overlap$gene_name, Microglia_interactome_AD_Kunkle2019 = ALS_Rheenen2021_5e8Microglia_interactome_overlap$Microglia_interactome_AD_Kunkle2019)

ADk_SCZ<-data.frame(gene_name=SCZ_Trubetskoy2022_5e12Microglia_interactome_overlap$gene_name, Microglia_interactome_AD_Kunkle2019 = SCZ_Trubetskoy2022_5e12Microglia_interactome_overlap$Microglia_interactome_AD_Kunkle2019)


ADk_pu1<-rbind(ADk_AD, ADk_ADk, ADk_PD, ADk_MS, ADk_ALS, ADk_SCZ)

#neurons 

ADk_ADk<-data.frame(gene_name=AD_Kunkle2019_5e8Neuronal_interactome_overlap$gene_name, Neuronal_interactome_AD_Kunkle2019 = AD_Kunkle2019_5e8Neuronal_interactome_overlap$Neuronal_interactome_AD_Kunkle2019)

ADk_AD<-data.frame(gene_name=AD_Jansen2019_5e8Neuronal_interactome_overlap$gene_name, Neuronal_interactome_AD_Kunkle2019 = AD_Jansen2019_5e8Neuronal_interactome_overlap$Neuronal_interactome_AD_Kunkle2019)

ADk_PD<-data.frame(gene_name=PD_Nalls2019proxy_5e8Neuronal_interactome_overlap$gene_name, Neuronal_interactome_AD_Kunkle2019 = PD_Nalls2019proxy_5e8Neuronal_interactome_overlap$Neuronal_interactome_AD_Kunkle2019)

#ADk_LBD<-data.frame(gene_name=LBD_chia2021_5e8Neuronal_interactome_overlap$gene_name, Neuronal_interactome_AD_Kunkle2019 = LBD_chia2021_5e8Neuronal_interactome_overlap$Neuronal_interactome_AD_Kunkle2019)

ADk_MS<-data.frame(gene_name=MS_Andlauer2016_5e8Neuronal_interactome_overlap$gene_name, Neuronal_interactome_AD_Kunkle2019 = MS_Andlauer2016_5e8Neuronal_interactome_overlap$Neuronal_interactome_AD_Kunkle2019)

ADk_ALS<-data.frame(gene_name=ALS_Rheenen2021_5e8Neuronal_interactome_overlap$gene_name, Neuronal_interactome_AD_Kunkle2019 = ALS_Rheenen2021_5e8Neuronal_interactome_overlap$Neuronal_interactome_AD_Kunkle2019)

ADk_SCZ<-data.frame(gene_name=SCZ_Trubetskoy2022_5e12Neuronal_interactome_overlap$gene_name, Neuronal_interactome_AD_Kunkle2019 = SCZ_Trubetskoy2022_5e12Neuronal_interactome_overlap$Neuronal_interactome_AD_Kunkle2019)

ADk_neun<-rbind(ADk_AD, ADk_ADk, ADk_PD, ADk_MS, ADk_ALS, ADk_SCZ)

#olig

ADk_ADk<-data.frame(gene_name=AD_Kunkle2019_5e8Oligo_interactome_overlap$gene_name, Oligo_interactome_AD_Kunkle2019 = AD_Kunkle2019_5e8Oligo_interactome_overlap$Oligo_interactome_AD_Kunkle2019)

ADk_AD<-data.frame(gene_name=AD_Jansen2019_5e8Oligo_interactome_overlap$gene_name, Oligo_interactome_AD_Kunkle2019 = AD_Jansen2019_5e8Oligo_interactome_overlap$Oligo_interactome_AD_Kunkle2019)

ADk_PD<-data.frame(gene_name=PD_Nalls2019proxy_5e8Oligo_interactome_overlap$gene_name, Oligo_interactome_AD_Kunkle2019 = PD_Nalls2019proxy_5e8Oligo_interactome_overlap$Oligo_interactome_AD_Kunkle2019)

#ADk_LBD<-data.frame(gene_name=LBD_chia2021_5e8Oligo_interactome_overlap$gene_name, Oligo_interactome_AD_Kunkle2019 = LBD_chia2021_5e8Oligo_interactome_overlap$Oligo_interactome_AD_Kunkle2019)

ADk_MS<-data.frame(gene_name=MS_Andlauer2016_5e8Oligo_interactome_overlap$gene_name, Oligo_interactome_AD_Kunkle2019 = MS_Andlauer2016_5e8Oligo_interactome_overlap$Oligo_interactome_AD_Kunkle2019)

ADk_ALS<-data.frame(gene_name=ALS_Rheenen2021_5e8Oligo_interactome_overlap$gene_name, Oligo_interactome_AD_Kunkle2019 = ALS_Rheenen2021_5e8Oligo_interactome_overlap$Oligo_interactome_AD_Kunkle2019)

ADk_SCZ<-data.frame(gene_name=SCZ_Trubetskoy2022_5e12Oligo_interactome_overlap$gene_name, Oligo_interactome_AD_Kunkle2019 = SCZ_Trubetskoy2022_5e12Oligo_interactome_overlap$Oligo_interactome_AD_Kunkle2019)


ADk_olig<-rbind(ADk_AD, ADk_ADk, ADk_PD, ADk_MS, ADk_ALS, ADk_SCZ)
```


#PD_nalls - combining all genes per disease together - the ones that overap with other diseases and 5e-8
```{r}
#micrglia
PD_AD<-data.frame(gene_name=AD_Jansen2019_5e8Microglia_interactome_overlap$gene_name, Microglia_interactome_PD_Nalls2019proxy = AD_Jansen2019_5e8Microglia_interactome_overlap$Microglia_interactome_PD_Nalls2019proxy)

PD_ADk<-data.frame(gene_name=AD_Kunkle2019_5e8Microglia_interactome_overlap$gene_name, Microglia_interactome_PD_Nalls2019proxy = AD_Kunkle2019_5e8Microglia_interactome_overlap$Microglia_interactome_PD_Nalls2019proxy)

PD_PD<-data.frame(gene_name=PD_Nalls2019proxy_5e8Microglia_interactome_overlap$gene_name, Microglia_interactome_PD_Nalls2019proxy = PD_Nalls2019proxy_5e8Microglia_interactome_overlap$Microglia_interactome_PD_Nalls2019proxy)

#PD_LBD<-data.frame(gene_name=LBD_chia2021_5e8Microglia_interactome_overlap$gene_name, Microglia_interactome_PD_Nalls2019proxy = LBD_chia2021_5e8Microglia_interactome_overlap$Microglia_interactome_PD_Nalls2019proxy)

PD_MS<-data.frame(gene_name=MS_Andlauer2016_5e8Microglia_interactome_overlap$gene_name, Microglia_interactome_PD_Nalls2019proxy = MS_Andlauer2016_5e8Microglia_interactome_overlap$Microglia_interactome_PD_Nalls2019proxy)

PD_ALS<-data.frame(gene_name=ALS_Rheenen2021_5e8Microglia_interactome_overlap$gene_name, Microglia_interactome_PD_Nalls2019proxy = ALS_Rheenen2021_5e8Microglia_interactome_overlap$Microglia_interactome_PD_Nalls2019proxy)

PD_SCZ<-data.frame(gene_name=SCZ_Trubetskoy2022_5e12Microglia_interactome_overlap$gene_name, Microglia_interactome_PD_Nalls2019proxy = SCZ_Trubetskoy2022_5e12Microglia_interactome_overlap$Microglia_interactome_PD_Nalls2019proxy)


PD_pu1<-rbind(PD_AD, PD_ADk, PD_PD, PD_MS, PD_ALS, PD_SCZ)

#neurons
PD_AD<-data.frame(gene_name=AD_Jansen2019_5e8Neuronal_interactome_overlap$gene_name, Neuronal_interactome_PD_Nalls2019proxy = AD_Jansen2019_5e8Neuronal_interactome_overlap$Neuronal_interactome_PD_Nalls2019proxy)

PD_ADk<-data.frame(gene_name=AD_Kunkle2019_5e8Neuronal_interactome_overlap$gene_name, Neuronal_interactome_PD_Nalls2019proxy = AD_Kunkle2019_5e8Neuronal_interactome_overlap$Neuronal_interactome_PD_Nalls2019proxy)

PD_PD<-data.frame(gene_name=PD_Nalls2019proxy_5e8Neuronal_interactome_overlap$gene_name, Neuronal_interactome_PD_Nalls2019proxy = PD_Nalls2019proxy_5e8Neuronal_interactome_overlap$Neuronal_interactome_PD_Nalls2019proxy)

#PD_LBD<-data.frame(gene_name=LBD_chia2021_5e8Neuronal_interactome_overlap$gene_name, Neuronal_interactome_PD_Nalls2019proxy = LBD_chia2021_5e8Neuronal_interactome_overlap$Neuronal_interactome_PD_Nalls2019proxy)

PD_MS<-data.frame(gene_name=MS_Andlauer2016_5e8Neuronal_interactome_overlap$gene_name, Neuronal_interactome_PD_Nalls2019proxy = MS_Andlauer2016_5e8Neuronal_interactome_overlap$Neuronal_interactome_PD_Nalls2019proxy)

PD_ALS<-data.frame(gene_name=ALS_Rheenen2021_5e8Neuronal_interactome_overlap$gene_name, Neuronal_interactome_PD_Nalls2019proxy = ALS_Rheenen2021_5e8Neuronal_interactome_overlap$Neuronal_interactome_PD_Nalls2019proxy)

PD_SCZ<-data.frame(gene_name=SCZ_Trubetskoy2022_5e12Neuronal_interactome_overlap$gene_name, Neuronal_interactome_PD_Nalls2019proxy = SCZ_Trubetskoy2022_5e12Neuronal_interactome_overlap$Neuronal_interactome_PD_Nalls2019proxy)


PD_neun<-rbind(PD_AD, PD_ADk, PD_PD, PD_MS, PD_ALS, PD_SCZ)

#oligo
PD_AD<-data.frame(gene_name=AD_Jansen2019_5e8Oligo_interactome_overlap$gene_name, Oligo_interactome_PD_Nalls2019proxy = AD_Jansen2019_5e8Oligo_interactome_overlap$Oligo_interactome_PD_Nalls2019proxy)

PD_ADk<-data.frame(gene_name=AD_Kunkle2019_5e8Oligo_interactome_overlap$gene_name, Oligo_interactome_PD_Nalls2019proxy = AD_Kunkle2019_5e8Oligo_interactome_overlap$Oligo_interactome_PD_Nalls2019proxy)

PD_PD<-data.frame(gene_name=PD_Nalls2019proxy_5e8Oligo_interactome_overlap$gene_name, Oligo_interactome_PD_Nalls2019proxy = PD_Nalls2019proxy_5e8Oligo_interactome_overlap$Oligo_interactome_PD_Nalls2019proxy)

#PD_LBD<-data.frame(gene_name=LBD_chia2021_5e8Oligo_interactome_overlap$gene_name, Oligo_interactome_PD_Nalls2019proxy = LBD_chia2021_5e8Oligo_interactome_overlap$Oligo_interactome_PD_Nalls2019proxy)

PD_MS<-data.frame(gene_name=MS_Andlauer2016_5e8Oligo_interactome_overlap$gene_name, Oligo_interactome_PD_Nalls2019proxy = MS_Andlauer2016_5e8Oligo_interactome_overlap$Oligo_interactome_PD_Nalls2019proxy)

PD_ALS<-data.frame(gene_name=ALS_Rheenen2021_5e8Oligo_interactome_overlap$gene_name, Oligo_interactome_PD_Nalls2019proxy = ALS_Rheenen2021_5e8Oligo_interactome_overlap$Oligo_interactome_PD_Nalls2019proxy)

PD_SCZ<-data.frame(gene_name=SCZ_Trubetskoy2022_5e12Oligo_interactome_overlap$gene_name, Oligo_interactome_PD_Nalls2019proxy = SCZ_Trubetskoy2022_5e12Oligo_interactome_overlap$Oligo_interactome_PD_Nalls2019proxy)


PD_olig<-rbind(PD_AD, PD_ADk, PD_PD, PD_MS, PD_ALS, PD_SCZ)
```


#LBD_chia - combining all genes per disease together - the ones that overap with other diseases and 5e-8

```{r}
#micrglia
LBD_AD<-data.frame(gene_name=AD_Jansen2019_5e8Microglia_interactome_overlap$gene_name, Microglia_interactome_LBD_chia2021 = AD_Jansen2019_5e8Microglia_interactome_overlap$Microglia_interactome_LBD_chia2021)

LBD_ADk<-data.frame(gene_name=AD_Kunkle2019_5e8Microglia_interactome_overlap$gene_name, Microglia_interactome_LBD_chia2021 = AD_Kunkle2019_5e8Microglia_interactome_overlap$Microglia_interactome_LBD_chia2021)

LBD_PD<-data.frame(gene_name=PD_Nalls2019proxy_5e8Microglia_interactome_overlap$gene_name, Microglia_interactome_LBD_chia2021 = PD_Nalls2019proxy_5e8Microglia_interactome_overlap$Microglia_interactome_LBD_chia2021)

LBD_LBD<-data.frame(gene_name=LBD_chia2021_5e8Microglia_interactome_overlap$gene_name, Microglia_interactome_LBD_chia2021 = LBD_chia2021_5e8Microglia_interactome_overlap$Microglia_interactome_LBD_chia2021)

LBD_MS<-data.frame(gene_name=MS_Andlauer2016_5e8Microglia_interactome_overlap$gene_name, Microglia_interactome_LBD_chia2021 = MS_Andlauer2016_5e8Microglia_interactome_overlap$Microglia_interactome_LBD_chia2021)

LBD_ALS<-data.frame(gene_name=ALS_Rheenen2021_5e8Microglia_interactome_overlap$gene_name, Microglia_interactome_LBD_chia2021 = ALS_Rheenen2021_5e8Microglia_interactome_overlap$Microglia_interactome_LBD_chia2021)

LBD_SCZ<-data.frame(gene_name=SCZ_Trubetskoy2022_5e12Microglia_interactome_overlap$gene_name, Microglia_interactome_LBD_chia2021 = SCZ_Trubetskoy2022_5e12Microglia_interactome_overlap$Microglia_interactome_LBD_chia2021)


LBD_pu1<-rbind(LBD_AD, LBD_ADk, LBD_PD, LBD_LBD, LBD_MS, LBD_ALS, LBD_SCZ)

#neurons

LBD_AD<-data.frame(gene_name=AD_Jansen2019_5e8Neuronal_interactome_overlap$gene_name, Neuronal_interactome_LBD_chia2021 = AD_Jansen2019_5e8Neuronal_interactome_overlap$Neuronal_interactome_LBD_chia2021)

LBD_ADk<-data.frame(gene_name=AD_Kunkle2019_5e8Neuronal_interactome_overlap$gene_name, Neuronal_interactome_LBD_chia2021 = AD_Kunkle2019_5e8Neuronal_interactome_overlap$Neuronal_interactome_LBD_chia2021)

LBD_PD<-data.frame(gene_name=PD_Nalls2019proxy_5e8Neuronal_interactome_overlap$gene_name, Neuronal_interactome_LBD_chia2021 = PD_Nalls2019proxy_5e8Neuronal_interactome_overlap$Neuronal_interactome_LBD_chia2021)

LBD_LBD<-data.frame(gene_name=LBD_chia2021_5e8Neuronal_interactome_overlap$gene_name, Neuronal_interactome_LBD_chia2021 = LBD_chia2021_5e8Neuronal_interactome_overlap$Neuronal_interactome_LBD_chia2021)

LBD_MS<-data.frame(gene_name=MS_Andlauer2016_5e8Neuronal_interactome_overlap$gene_name, Neuronal_interactome_LBD_chia2021 = MS_Andlauer2016_5e8Neuronal_interactome_overlap$Neuronal_interactome_LBD_chia2021)

LBD_ALS<-data.frame(gene_name=ALS_Rheenen2021_5e8Neuronal_interactome_overlap$gene_name, Neuronal_interactome_LBD_chia2021 = ALS_Rheenen2021_5e8Neuronal_interactome_overlap$Neuronal_interactome_LBD_chia2021)

LBD_SCZ<-data.frame(gene_name=SCZ_Trubetskoy2022_5e12Neuronal_interactome_overlap$gene_name, Neuronal_interactome_LBD_chia2021 = SCZ_Trubetskoy2022_5e12Neuronal_interactome_overlap$Neuronal_interactome_LBD_chia2021)

LBD_neun<-rbind(LBD_AD, LBD_ADk, LBD_PD, LBD_LBD, LBD_MS, LBD_ALS, LBD_SCZ)

#oligo

LBD_AD<-data.frame(gene_name=AD_Jansen2019_5e8Oligo_interactome_overlap$gene_name, Oligo_interactome_LBD_chia2021 = AD_Jansen2019_5e8Oligo_interactome_overlap$Oligo_interactome_LBD_chia2021)

LBD_ADk<-data.frame(gene_name=AD_Kunkle2019_5e8Oligo_interactome_overlap$gene_name, Oligo_interactome_LBD_chia2021 = AD_Kunkle2019_5e8Oligo_interactome_overlap$Oligo_interactome_LBD_chia2021)

LBD_PD<-data.frame(gene_name=PD_Nalls2019proxy_5e8Oligo_interactome_overlap$gene_name, Oligo_interactome_LBD_chia2021 = PD_Nalls2019proxy_5e8Oligo_interactome_overlap$Oligo_interactome_LBD_chia2021)

LBD_LBD<-data.frame(gene_name=LBD_chia2021_5e8Oligo_interactome_overlap$gene_name, Oligo_interactome_LBD_chia2021 = LBD_chia2021_5e8Oligo_interactome_overlap$Oligo_interactome_LBD_chia2021)

LBD_MS<-data.frame(gene_name=MS_Andlauer2016_5e8Oligo_interactome_overlap$gene_name, Oligo_interactome_LBD_chia2021 = MS_Andlauer2016_5e8Oligo_interactome_overlap$Oligo_interactome_LBD_chia2021)

LBD_ALS<-data.frame(gene_name=ALS_Rheenen2021_5e8Oligo_interactome_overlap$gene_name, Oligo_interactome_LBD_chia2021 = ALS_Rheenen2021_5e8Oligo_interactome_overlap$Oligo_interactome_LBD_chia2021)

LBD_SCZ<-data.frame(gene_name=SCZ_Trubetskoy2022_5e12Oligo_interactome_overlap$gene_name, Oligo_interactome_LBD_chia2021 = SCZ_Trubetskoy2022_5e12Oligo_interactome_overlap$Oligo_interactome_LBD_chia2021)

LBD_olig<-rbind(LBD_AD, LBD_ADk, LBD_PD, LBD_LBD, LBD_MS, LBD_ALS, LBD_SCZ)

```

#MS - combining all genes per disease together - the ones that overap with other diseases and 5e-8
```{r}
#micrglia
MS_AD<-data.frame(gene_name=AD_Jansen2019_5e8Microglia_interactome_overlap$gene_name, Microglia_interactome_MS_Andlauer2016 = AD_Jansen2019_5e8Microglia_interactome_overlap$Microglia_interactome_MS_Andlauer2016)

MS_ADk<-data.frame(gene_name=AD_Kunkle2019_5e8Microglia_interactome_overlap$gene_name, Microglia_interactome_MS_Andlauer2016 = AD_Kunkle2019_5e8Microglia_interactome_overlap$Microglia_interactome_MS_Andlauer2016)

MS_PD<-data.frame(gene_name=PD_Nalls2019proxy_5e8Microglia_interactome_overlap$gene_name, Microglia_interactome_MS_Andlauer2016 = PD_Nalls2019proxy_5e8Microglia_interactome_overlap$Microglia_interactome_MS_Andlauer2016)

#MS_LBD<-data.frame(gene_name=LBD_chia2021_5e8Microglia_interactome_overlap$gene_name, Microglia_interactome_MS_Andlauer2016 = LBD_chia2021_5e8Microglia_interactome_overlap$Microglia_interactome_MS_Andlauer2016)

MS_MS<-data.frame(gene_name=MS_Andlauer2016_5e8Microglia_interactome_overlap$gene_name, Microglia_interactome_MS_Andlauer2016 = MS_Andlauer2016_5e8Microglia_interactome_overlap$Microglia_interactome_MS_Andlauer2016)

MS_ALS<-data.frame(gene_name=ALS_Rheenen2021_5e8Microglia_interactome_overlap$gene_name, Microglia_interactome_MS_Andlauer2016 = ALS_Rheenen2021_5e8Microglia_interactome_overlap$Microglia_interactome_MS_Andlauer2016)

MS_SCZ<-data.frame(gene_name=SCZ_Trubetskoy2022_5e12Microglia_interactome_overlap$gene_name, Microglia_interactome_MS_Andlauer2016 = SCZ_Trubetskoy2022_5e12Microglia_interactome_overlap$Microglia_interactome_MS_Andlauer2016)



MS_pu1<-rbind(MS_AD, MS_ADk, MS_PD, MS_MS, MS_ALS, MS_SCZ)

#neurons

MS_AD<-data.frame(gene_name=AD_Jansen2019_5e8Neuronal_interactome_overlap$gene_name, Neuronal_interactome_MS_Andlauer2016 = AD_Jansen2019_5e8Neuronal_interactome_overlap$Neuronal_interactome_MS_Andlauer2016)

MS_ADk<-data.frame(gene_name=AD_Kunkle2019_5e8Neuronal_interactome_overlap$gene_name, Neuronal_interactome_MS_Andlauer2016 = AD_Kunkle2019_5e8Neuronal_interactome_overlap$Neuronal_interactome_MS_Andlauer2016)

MS_PD<-data.frame(gene_name=PD_Nalls2019proxy_5e8Neuronal_interactome_overlap$gene_name, Neuronal_interactome_MS_Andlauer2016 = PD_Nalls2019proxy_5e8Neuronal_interactome_overlap$Neuronal_interactome_MS_Andlauer2016)

#MS_LBD<-data.frame(gene_name=LBD_chia2021_5e8Neuronal_interactome_overlap$gene_name, Neuronal_interactome_MS_Andlauer2016 = LBD_chia2021_5e8Neuronal_interactome_overlap$Neuronal_interactome_MS_Andlauer2016)

MS_MS<-data.frame(gene_name=MS_Andlauer2016_5e8Neuronal_interactome_overlap$gene_name, Neuronal_interactome_MS_Andlauer2016 = MS_Andlauer2016_5e8Neuronal_interactome_overlap$Neuronal_interactome_MS_Andlauer2016)

MS_ALS<-data.frame(gene_name=ALS_Rheenen2021_5e8Neuronal_interactome_overlap$gene_name, Neuronal_interactome_MS_Andlauer2016 = ALS_Rheenen2021_5e8Neuronal_interactome_overlap$Neuronal_interactome_MS_Andlauer2016)

MS_SCZ<-data.frame(gene_name=SCZ_Trubetskoy2022_5e12Neuronal_interactome_overlap$gene_name, Neuronal_interactome_MS_Andlauer2016 = SCZ_Trubetskoy2022_5e12Neuronal_interactome_overlap$Neuronal_interactome_MS_Andlauer2016)

MS_neun<-rbind(MS_AD, MS_ADk, MS_PD, MS_MS, MS_ALS, MS_SCZ)

#oligo 
MS_AD<-data.frame(gene_name=AD_Jansen2019_5e8Oligo_interactome_overlap$gene_name, Oligo_interactome_MS_Andlauer2016 = AD_Jansen2019_5e8Oligo_interactome_overlap$Oligo_interactome_MS_Andlauer2016)

MS_ADk<-data.frame(gene_name=AD_Kunkle2019_5e8Oligo_interactome_overlap$gene_name, Oligo_interactome_MS_Andlauer2016 = AD_Kunkle2019_5e8Oligo_interactome_overlap$Oligo_interactome_MS_Andlauer2016)

MS_PD<-data.frame(gene_name=PD_Nalls2019proxy_5e8Oligo_interactome_overlap$gene_name, Oligo_interactome_MS_Andlauer2016 = PD_Nalls2019proxy_5e8Oligo_interactome_overlap$Oligo_interactome_MS_Andlauer2016)

#MS_LBD<-data.frame(gene_name=LBD_chia2021_5e8Oligo_interactome_overlap$gene_name, Oligo_interactome_MS_Andlauer2016 = LBD_chia2021_5e8Oligo_interactome_overlap$Oligo_interactome_MS_Andlauer2016)

MS_MS<-data.frame(gene_name=MS_Andlauer2016_5e8Oligo_interactome_overlap$gene_name, Oligo_interactome_MS_Andlauer2016 = MS_Andlauer2016_5e8Oligo_interactome_overlap$Oligo_interactome_MS_Andlauer2016)

MS_ALS<-data.frame(gene_name=ALS_Rheenen2021_5e8Oligo_interactome_overlap$gene_name, Oligo_interactome_MS_Andlauer2016 = ALS_Rheenen2021_5e8Oligo_interactome_overlap$Oligo_interactome_MS_Andlauer2016)

MS_SCZ<-data.frame(gene_name=SCZ_Trubetskoy2022_5e12Oligo_interactome_overlap$gene_name, Oligo_interactome_MS_Andlauer2016 = SCZ_Trubetskoy2022_5e12Oligo_interactome_overlap$Oligo_interactome_MS_Andlauer2016)

MS_olig<-rbind(MS_AD, MS_ADk, MS_PD, MS_MS, MS_ALS, MS_SCZ)
```

#ALS - combining all genes per disease together - the ones that overap with other diseases and 5e-8
```{r}
#micrglia
ALS_AD<-data.frame(gene_name=AD_Jansen2019_5e8Microglia_interactome_overlap$gene_name, Microglia_interactome_ALS_Rheenen2021 = AD_Jansen2019_5e8Microglia_interactome_overlap$Microglia_interactome_ALS_Rheenen2021)

ALS_ADk<-data.frame(gene_name=AD_Kunkle2019_5e8Microglia_interactome_overlap$gene_name, Microglia_interactome_ALS_Rheenen2021 = AD_Kunkle2019_5e8Microglia_interactome_overlap$Microglia_interactome_ALS_Rheenen2021)

ALS_PD<-data.frame(gene_name=PD_Nalls2019proxy_5e8Microglia_interactome_overlap$gene_name, Microglia_interactome_ALS_Rheenen2021 = PD_Nalls2019proxy_5e8Microglia_interactome_overlap$Microglia_interactome_ALS_Rheenen2021)

#ALS_LBD<-data.frame(gene_name=LBD_chia2021_5e8Microglia_interactome_overlap$gene_name, Microglia_interactome_ALS_Rheenen2021 = LBD_chia2021_5e8Microglia_interactome_overlap$Microglia_interactome_ALS_Rheenen2021)

ALS_MS<-data.frame(gene_name=MS_Andlauer2016_5e8Microglia_interactome_overlap$gene_name, Microglia_interactome_ALS_Rheenen2021 = MS_Andlauer2016_5e8Microglia_interactome_overlap$Microglia_interactome_ALS_Rheenen2021)

ALS_ALS<-data.frame(gene_name=ALS_Rheenen2021_5e8Microglia_interactome_overlap$gene_name, Microglia_interactome_ALS_Rheenen2021 = ALS_Rheenen2021_5e8Microglia_interactome_overlap$Microglia_interactome_ALS_Rheenen2021)

ALS_SCZ<-data.frame(gene_name=SCZ_Trubetskoy2022_5e12Microglia_interactome_overlap$gene_name, Microglia_interactome_ALS_Rheenen2021 = SCZ_Trubetskoy2022_5e12Microglia_interactome_overlap$Microglia_interactome_ALS_Rheenen2021)


ALS_pu1<-rbind(ALS_AD, ALS_ADk, ALS_PD, ALS_MS, ALS_ALS, ALS_SCZ)

#neurons

ALS_AD<-data.frame(gene_name=AD_Jansen2019_5e8Neuronal_interactome_overlap$gene_name, Neuronal_interactome_ALS_Rheenen2021 = AD_Jansen2019_5e8Neuronal_interactome_overlap$Neuronal_interactome_ALS_Rheenen2021)

ALS_ADk<-data.frame(gene_name=AD_Kunkle2019_5e8Neuronal_interactome_overlap$gene_name, Neuronal_interactome_ALS_Rheenen2021 = AD_Kunkle2019_5e8Neuronal_interactome_overlap$Neuronal_interactome_ALS_Rheenen2021)

ALS_PD<-data.frame(gene_name=PD_Nalls2019proxy_5e8Neuronal_interactome_overlap$gene_name, Neuronal_interactome_ALS_Rheenen2021 = PD_Nalls2019proxy_5e8Neuronal_interactome_overlap$Neuronal_interactome_ALS_Rheenen2021)

#ALS_LBD<-data.frame(gene_name=LBD_chia2021_5e8Neuronal_interactome_overlap$gene_name, Neuronal_interactome_ALS_Rheenen2021 = LBD_chia2021_5e8Neuronal_interactome_overlap$Neuronal_interactome_ALS_Rheenen2021)

ALS_MS<-data.frame(gene_name=MS_Andlauer2016_5e8Neuronal_interactome_overlap$gene_name, Neuronal_interactome_ALS_Rheenen2021 = MS_Andlauer2016_5e8Neuronal_interactome_overlap$Neuronal_interactome_ALS_Rheenen2021)

ALS_ALS<-data.frame(gene_name=ALS_Rheenen2021_5e8Neuronal_interactome_overlap$gene_name, Neuronal_interactome_ALS_Rheenen2021 = ALS_Rheenen2021_5e8Neuronal_interactome_overlap$Neuronal_interactome_ALS_Rheenen2021)

ALS_SCZ<-data.frame(gene_name=SCZ_Trubetskoy2022_5e12Neuronal_interactome_overlap$gene_name, Neuronal_interactome_ALS_Rheenen2021 = SCZ_Trubetskoy2022_5e12Neuronal_interactome_overlap$Neuronal_interactome_ALS_Rheenen2021)

ALS_neun<-rbind(ALS_AD, ALS_ADk, ALS_PD, ALS_MS, ALS_ALS, ALS_SCZ)

#oligo

ALS_AD<-data.frame(gene_name=AD_Jansen2019_5e8Oligo_interactome_overlap$gene_name, Oligo_interactome_ALS_Rheenen2021 = AD_Jansen2019_5e8Oligo_interactome_overlap$Oligo_interactome_ALS_Rheenen2021)

ALS_ADk<-data.frame(gene_name=AD_Kunkle2019_5e8Oligo_interactome_overlap$gene_name, Oligo_interactome_ALS_Rheenen2021 = AD_Kunkle2019_5e8Oligo_interactome_overlap$Oligo_interactome_ALS_Rheenen2021)

ALS_PD<-data.frame(gene_name=PD_Nalls2019proxy_5e8Oligo_interactome_overlap$gene_name, Oligo_interactome_ALS_Rheenen2021 = PD_Nalls2019proxy_5e8Oligo_interactome_overlap$Oligo_interactome_ALS_Rheenen2021)

#ALS_LBD<-data.frame(gene_name=LBD_chia2021_5e8Oligo_interactome_overlap$gene_name, Oligo_interactome_ALS_Rheenen2021 = LBD_chia2021_5e8Oligo_interactome_overlap$Oligo_interactome_ALS_Rheenen2021)

ALS_MS<-data.frame(gene_name=MS_Andlauer2016_5e8Oligo_interactome_overlap$gene_name, Oligo_interactome_ALS_Rheenen2021 = MS_Andlauer2016_5e8Oligo_interactome_overlap$Oligo_interactome_ALS_Rheenen2021)

ALS_ALS<-data.frame(gene_name=ALS_Rheenen2021_5e8Oligo_interactome_overlap$gene_name, Oligo_interactome_ALS_Rheenen2021 = ALS_Rheenen2021_5e8Oligo_interactome_overlap$Oligo_interactome_ALS_Rheenen2021)

ALS_SCZ<-data.frame(gene_name=SCZ_Trubetskoy2022_5e12Oligo_interactome_overlap$gene_name, Oligo_interactome_ALS_Rheenen2021 = SCZ_Trubetskoy2022_5e12Oligo_interactome_overlap$Oligo_interactome_ALS_Rheenen2021)

ALS_olig<-rbind(ALS_AD, ALS_ADk, ALS_PD, ALS_MS, ALS_ALS, ALS_SCZ)
```
#SCZ - combining all genes per disease together - the ones that overap with other diseases and 5e-8

```{r}
#micrglia
SCZ_AD<-data.frame(gene_name=AD_Jansen2019_5e8Microglia_interactome_overlap$gene_name, Microglia_interactome_SCZ_Trubetskoy2022 = AD_Jansen2019_5e8Microglia_interactome_overlap$Microglia_interactome_SCZ_Trubetskoy2022)

SCZ_ADk<-data.frame(gene_name=AD_Kunkle2019_5e8Microglia_interactome_overlap$gene_name, Microglia_interactome_SCZ_Trubetskoy2022 = AD_Kunkle2019_5e8Microglia_interactome_overlap$Microglia_interactome_SCZ_Trubetskoy2022)

SCZ_PD<-data.frame(gene_name=PD_Nalls2019proxy_5e8Microglia_interactome_overlap$gene_name, Microglia_interactome_SCZ_Trubetskoy2022 = PD_Nalls2019proxy_5e8Microglia_interactome_overlap$Microglia_interactome_SCZ_Trubetskoy2022)

#SCZ_LBD<-data.frame(gene_name=LBD_chia2021_5e8Microglia_interactome_overlap$gene_name, Microglia_interactome_SCZ_Trubetskoy2022 = LBD_chia2021_5e8Microglia_interactome_overlap$Microglia_interactome_SCZ_Trubetskoy2022)

SCZ_MS<-data.frame(gene_name=MS_Andlauer2016_5e8Microglia_interactome_overlap$gene_name, Microglia_interactome_SCZ_Trubetskoy2022 = MS_Andlauer2016_5e8Microglia_interactome_overlap$Microglia_interactome_SCZ_Trubetskoy2022)

SCZ_ALS<-data.frame(gene_name=ALS_Rheenen2021_5e8Microglia_interactome_overlap$gene_name, Microglia_interactome_SCZ_Trubetskoy2022 = ALS_Rheenen2021_5e8Microglia_interactome_overlap$Microglia_interactome_SCZ_Trubetskoy2022)

SCZ_SCZ<-data.frame(gene_name=SCZ_Trubetskoy2022_5e12Microglia_interactome_overlap$gene_name, Microglia_interactome_SCZ_Trubetskoy2022 = SCZ_Trubetskoy2022_5e12Microglia_interactome_overlap$Microglia_interactome_SCZ_Trubetskoy2022)


SCZ_pu1<-rbind(SCZ_AD, SCZ_ADk, SCZ_PD, SCZ_MS, SCZ_ALS, SCZ_SCZ)

#neurons
SCZ_AD<-data.frame(gene_name=AD_Jansen2019_5e8Neuronal_interactome_overlap$gene_name, Neuronal_interactome_SCZ_Trubetskoy2022 = AD_Jansen2019_5e8Neuronal_interactome_overlap$Neuronal_interactome_SCZ_Trubetskoy2022)

SCZ_ADk<-data.frame(gene_name=AD_Kunkle2019_5e8Neuronal_interactome_overlap$gene_name, Neuronal_interactome_SCZ_Trubetskoy2022 = AD_Kunkle2019_5e8Neuronal_interactome_overlap$Neuronal_interactome_SCZ_Trubetskoy2022)

SCZ_PD<-data.frame(gene_name=PD_Nalls2019proxy_5e8Neuronal_interactome_overlap$gene_name, Neuronal_interactome_SCZ_Trubetskoy2022 = PD_Nalls2019proxy_5e8Neuronal_interactome_overlap$Neuronal_interactome_SCZ_Trubetskoy2022)

#SCZ_LBD<-data.frame(gene_name=LBD_chia2021_5e8Neuronal_interactome_overlap$gene_name, Neuronal_interactome_SCZ_Trubetskoy2022 = LBD_chia2021_5e8Neuronal_interactome_overlap$Neuronal_interactome_SCZ_Trubetskoy2022)

SCZ_MS<-data.frame(gene_name=MS_Andlauer2016_5e8Neuronal_interactome_overlap$gene_name, Neuronal_interactome_SCZ_Trubetskoy2022 = MS_Andlauer2016_5e8Neuronal_interactome_overlap$Neuronal_interactome_SCZ_Trubetskoy2022)

SCZ_ALS<-data.frame(gene_name=ALS_Rheenen2021_5e8Neuronal_interactome_overlap$gene_name, Neuronal_interactome_SCZ_Trubetskoy2022 = ALS_Rheenen2021_5e8Neuronal_interactome_overlap$Neuronal_interactome_SCZ_Trubetskoy2022)

SCZ_SCZ<-data.frame(gene_name=SCZ_Trubetskoy2022_5e12Neuronal_interactome_overlap$gene_name, Neuronal_interactome_SCZ_Trubetskoy2022 = SCZ_Trubetskoy2022_5e12Neuronal_interactome_overlap$Neuronal_interactome_SCZ_Trubetskoy2022)


SCZ_neun<-rbind(SCZ_AD, SCZ_ADk, SCZ_PD, SCZ_MS, SCZ_ALS, SCZ_SCZ)

#olig

SCZ_AD<-data.frame(gene_name=AD_Jansen2019_5e8Oligo_interactome_overlap$gene_name, Oligo_interactome_SCZ_Trubetskoy2022 = AD_Jansen2019_5e8Oligo_interactome_overlap$Oligo_interactome_SCZ_Trubetskoy2022)

SCZ_ADk<-data.frame(gene_name=AD_Kunkle2019_5e8Oligo_interactome_overlap$gene_name, Oligo_interactome_SCZ_Trubetskoy2022 = AD_Kunkle2019_5e8Oligo_interactome_overlap$Oligo_interactome_SCZ_Trubetskoy2022)

SCZ_PD<-data.frame(gene_name=PD_Nalls2019proxy_5e8Oligo_interactome_overlap$gene_name, Oligo_interactome_SCZ_Trubetskoy2022 = PD_Nalls2019proxy_5e8Oligo_interactome_overlap$Oligo_interactome_SCZ_Trubetskoy2022)

#SCZ_LBD<-data.frame(gene_name=LBD_chia2021_5e8Oligo_interactome_overlap$gene_name, Oligo_interactome_SCZ_Trubetskoy2022 = LBD_chia2021_5e8Oligo_interactome_overlap$Oligo_interactome_SCZ_Trubetskoy2022)

SCZ_MS<-data.frame(gene_name=MS_Andlauer2016_5e8Oligo_interactome_overlap$gene_name, Oligo_interactome_SCZ_Trubetskoy2022 = MS_Andlauer2016_5e8Oligo_interactome_overlap$Oligo_interactome_SCZ_Trubetskoy2022)

SCZ_ALS<-data.frame(gene_name=ALS_Rheenen2021_5e8Oligo_interactome_overlap$gene_name, Oligo_interactome_SCZ_Trubetskoy2022 = ALS_Rheenen2021_5e8Oligo_interactome_overlap$Oligo_interactome_SCZ_Trubetskoy2022)

SCZ_SCZ<-data.frame(gene_name=SCZ_Trubetskoy2022_5e12Oligo_interactome_overlap$gene_name, Oligo_interactome_SCZ_Trubetskoy2022 = SCZ_Trubetskoy2022_5e12Oligo_interactome_overlap$Oligo_interactome_SCZ_Trubetskoy2022)


SCZ_olig<-rbind(SCZ_AD, SCZ_ADk, SCZ_PD, SCZ_MS, SCZ_ALS, SCZ_SCZ)
```



#PU1 - combining all genes per disease together - the ones that overap with other diseases and 5e-8
```{r}

pu1<-cbind(AD_pu1, ADk_pu1, PD_pu1, MS_pu1, ALS_pu1, SCZ_pu1)
pu1<-pu1[-c(3,5,7,9,11,13)]

pu1$Microglia_interactome_AD_Jansen2019<-round(x = -log10(pu1$Microglia_interactome_AD_Jansen2019), digits = 2)
pu1$Microglia_interactome_AD_Kunkle2019<-round(x = -log10(pu1$Microglia_interactome_AD_Kunkle2019), digits = 2)
pu1$Microglia_interactome_PD_Nalls2019proxy<-round(x = -log10(pu1$Microglia_interactome_PD_Nalls2019proxy), digits = 2)
#pu1$Microglia_interactome_LBD_chia2021<-round(x = -log10(pu1$Microglia_interactome_LBD_chia2021), digits = 2)
pu1$Microglia_interactome_MS_Andlauer2016<-round(x = -log10(pu1$Microglia_interactome_MS_Andlauer2016), digits = 2)
pu1$Microglia_interactome_ALS_Rheenen2021<-round(x = -log10(pu1$Microglia_interactome_ALS_Rheenen2021), digits = 2)
pu1$Microglia_interactome_SCZ_Trubetskoy2022<-round(x = -log10(pu1$Microglia_interactome_SCZ_Trubetskoy2022), digits = 2)

pu1<-unique(pu1)
my_patterns <- c("Y_RNA")
#filter for rows where status column contains one of several strings
pu1 <- pu1 %>% filter(!grepl(paste(my_patterns, collapse='|'), gene_name))
rownames(pu1)<-pu1$gene_name
pu1<-pu1[,-1]
pu1 <- replace(pu1, is.na(pu1), 0)

pu1_2<-transpose(pu1)
rownames(pu1_2)<-colnames(pu1)
colnames(pu1_2)<-rownames(pu1)
```

```{r}
annotation_row<-data.frame(DiseaseType = c(rep(c("AD_Jansen"), times=1), rep(c("AD_Kunkle"), times=1), rep(c("PD"), times=1), rep(c("MS"), times=1), rep(c("ALS"), times=1), rep(c("SCZ"), times=1)))

rownames(annotation_row) = rownames(pu1_2)

ann_colors = list(DiseaseType = c(AD_Jansen="darkorange2", AD_Kunkle = "goldenrod1",  PD="slateblue3", MS="midnightblue", ALS="orangered4", SCZ="olivedrab3"))

pheatmap(mat = pu1_2, 
         color = c("white","pink1", "palevioletred1", "hotpink3", "darkorchid4"), 
        breaks = c(1, 1.30103, 2, 3, 4, 5),
        display_numbers = F, 
        number_color = "black", 
        fontsize_number = 10,
        number_format =  "%.1f",
        border_color = "grey88",
        annotation_row = annotation_row,
        annotation_colors = ann_colors,  
        angle_col = 90, 
        treeheight_row = 5, 
        treeheight_col = 10,
        cluster_rows = T, 
        cluster_cols = T, 
        show_rownames = F,
        show_colnames =T, 
        cellwidth = 4, 
        cellheight = 4,
        fontsize = 4, 
        fontsize_row = 4, 
        fontsize_col = 3,
        height = 2, 
        width = 9, main = "Microglia all genes",
filename = "~/HMAGMA_Protocol/results/graphs/pheatmap/microglia_pheatmap_v7.pdf")
```

#neun - combining all genes per disease together - the ones that overap with other diseases and 5e-8
```{r}

neun<-cbind(AD_neun, ADk_neun, PD_neun, MS_neun, ALS_neun, SCZ_neun)
neun<-neun[-c(3,5,7,9,11,13)]

neun$Neuronal_interactome_AD_Jansen2019<-round(x = -log10(neun$Neuronal_interactome_AD_Jansen2019), digits = 2)
neun$Neuronal_interactome_AD_Kunkle2019<-round(x = -log10(neun$Neuronal_interactome_AD_Kunkle2019), digits = 2)
neun$Neuronal_interactome_PD_Nalls2019proxy<-round(x = -log10(neun$Neuronal_interactome_PD_Nalls2019proxy), digits = 2)
#neun$Neuronal_interactome_LBD_chia2021<-round(x = -log10(neun$Neuronal_interactome_LBD_chia2021), digits = 2)
neun$Neuronal_interactome_MS_Andlauer2016<-round(x = -log10(neun$Neuronal_interactome_MS_Andlauer2016), digits = 2)
neun$Neuronal_interactome_ALS_Rheenen2021<-round(x = -log10(neun$Neuronal_interactome_ALS_Rheenen2021), digits = 2)
neun$Neuronal_interactome_SCZ_Trubetskoy2022<-round(x = -log10(neun$Neuronal_interactome_SCZ_Trubetskoy2022), digits = 2)

neun<-unique(neun)
#my_patterns <- c("SNORA63", "SNORD19", "SNORD19B", "snoU13", "Y_RNA", "MATR3")
#filter for rows where status column contains one of several strings
#neun <- neun %>% filter(!grepl(paste(my_patterns, collapse='|'), gene_name))
rownames(neun)<-neun$gene_name
neun<-neun[,-1]
neun <- replace(neun, is.na(neun), 0)

neun_2<-transpose(neun)
rownames(neun_2)<-colnames(neun)
colnames(neun_2)<-rownames(neun)
```

```{r}
annotation_row<-data.frame(DiseaseType = c(rep(c("AD_Jansen"), times=1), rep(c("AD_Kunkle"), times=1), rep(c("PD"), times=1), rep(c("MS"), times=1), rep(c("ALS"), times=1), rep(c("SCZ"), times=1)))

rownames(annotation_row) = rownames(neun_2)

ann_colors = list(DiseaseType = c(AD_Jansen="darkorange2", AD_Kunkle = "goldenrod1",  PD="slateblue3", MS="midnightblue", ALS="orangered4", SCZ="olivedrab3"))

pheatmap(mat = neun_2, 
         color = c("white","pink1", "palevioletred1", "hotpink3", "darkorchid4"), 
         breaks = c(1, 1.30103, 2, 3, 4, 5),
         display_numbers = F, 
         number_color = "black", 
         fontsize_number = 10,
         number_format =  "%.1f",
         border_color = "grey88",
         annotation_row = annotation_row,
         annotation_colors = ann_colors,  
         angle_col = 90, 
         treeheight_row = 5, 
         treeheight_col = 10,
         cluster_rows = T, 
         cluster_cols = T, 
         show_rownames = F,
         show_colnames =T, 
         cellwidth = 4, 
         cellheight = 4,
         fontsize = 4, 
         fontsize_row = 4, 
         fontsize_col = 3,
         height = 2, 
         width = 9, main = "Neurons all genes",
         filename = "~/HMAGMA_Protocol/results/graphs/pheatmap/neurons_pheatmap_v7.pdf")
```

#olig - combining all genes per disease together - the ones that overap with other diseases and 5e-8
```{r}

olig<-cbind(AD_olig, ADk_olig, PD_olig, MS_olig, ALS_olig, SCZ_olig)
olig<-olig[-c(3,5,7,9,11,13)]

olig$Oligo_interactome_AD_Jansen2019<-round(x = -log10(olig$Oligo_interactome_AD_Jansen2019), digits = 2)
olig$Oligo_interactome_AD_Kunkle2019<-round(x = -log10(olig$Oligo_interactome_AD_Kunkle2019), digits = 2)
olig$Oligo_interactome_PD_Nalls2019proxy<-round(x = -log10(olig$Oligo_interactome_PD_Nalls2019proxy), digits = 2)
#olig$Oligo_interactome_LBD_chia2021<-round(x = -log10(olig$Oligo_interactome_LBD_chia2021), digits = 2)
olig$Oligo_interactome_MS_Andlauer2016<-round(x = -log10(olig$Oligo_interactome_MS_Andlauer2016), digits = 2)
olig$Oligo_interactome_ALS_Rheenen2021<-round(x = -log10(olig$Oligo_interactome_ALS_Rheenen2021), digits = 2)
olig$Oligo_interactome_SCZ_Trubetskoy2022<-round(x = -log10(olig$Oligo_interactome_SCZ_Trubetskoy2022), digits = 2)

olig<-unique(olig)
#my_patterns <- c("SNORA63", "SNORD19", "SNORD19B", "snoU13", "Y_RNA", "MATR3")
#filter for rows where status column contains one of several strings
#olig <- olig %>% filter(!grepl(paste(my_patterns, collapse='|'), gene_name))
rownames(olig)<-olig$gene_name
olig<-olig[,-1]
olig <- replace(olig, is.na(olig), 0)

olig_2<-transpose(olig)
rownames(olig_2)<-colnames(olig)
colnames(olig_2)<-rownames(olig)
```

```{r}
annotation_row<-data.frame(DiseaseType = c(rep(c("AD_Jansen"), times=1), rep(c("AD_Kunkle"), times=1), rep(c("PD"), times=1), rep(c("MS"), times=1), rep(c("ALS"), times=1), rep(c("SCZ"), times=1)))

rownames(annotation_row) = rownames(olig_2)

ann_colors = list(DiseaseType = c(AD_Jansen="darkorange2", AD_Kunkle = "goldenrod1",  PD="slateblue3", MS="midnightblue", ALS="orangered4", SCZ="olivedrab3"))

pheatmap(mat = olig_2, 
         color = c("white","pink1", "palevioletred1", "hotpink3", "darkorchid4"), 
         breaks = c(1, 1.30103, 2, 3, 4, 5),
         display_numbers = F, 
         number_color = "black", 
         fontsize_number = 10,
         number_format =  "%.1f",
         border_color = "grey88",
         annotation_row = annotation_row,
         annotation_colors = ann_colors,  
         angle_col = 90, 
         treeheight_row = 5, 
         treeheight_col = 10,
         cluster_rows = T, 
         cluster_cols = T, 
         show_rownames = F,
         show_colnames =T, 
         cellwidth = 4, 
         cellheight = 4,
         fontsize = 4, 
         fontsize_row = 4, 
         fontsize_col = 3,
         height = 2, 
         width = 9, main = "Oligo all genes",
         filename = "~/HMAGMA_Protocol/results/graphs/pheatmap/oligo_pheatmap_v7.pdf")
```
